---
title: "Progress_Report_Airbnb"
date: "10/26/2020"
output:
  rmarkdown::html_vignette: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Aribnb_New_York_city    
## Group member:Yan Zhang, Yuncheng Shi,Yiyao Wang

# Description

Aribnb New York is a data set about the information of home stay in New York. It include name of house, type of house, owner's name, location and number of reviews. According to our shiny app, we want to help the user screen the houses that meet the criteria, study the relationship between variables and conduct statistical analysis.

```{block}
This description seems to focused on just description displays and not enough analysis. Would rather reduce the options for graphical analysis to the basics point, histogram, boxplots and address the following:

1. Try to predict what the rate should be for the chosen house based on a linear model and see if the rate is within a confidence interval. Allow the user to select up to three variables of interest as explanatory variables such as neighborhood, star rating and minimum stay or others. Then show the results for those variables. Filter the data on those variables, run the model and show the results.

A possible second problem. Do a text analysis on the English language reviews and offer a sentiment score as an alternative to the rating in the linear model if there are more than 20 reviews on a property


```
# Data source

[Aribnb_New_York_city](http://insideairbnb.com/get-the-data.html) 

```{block}
NIce data set. Be sure to use the detailed listing file
```


# Overall Layout

We plan to create three main tabs.

## map page

The first tab is map. It include the title, the filter on the left, the map with eligible houses on the right. The filter can be name, host name,neighborhood,price, room type and so on. Users can use the filter to choose the house the want to live.

```{block}
Make sure you keep the selected listing so you can show it in the graphics below as a vline (histograms), or a point, etc..
```


## plot and test page

As we have shown the users which rooms are satisfied to them on the map based on their preference, we are going to do some statistics in the second page. In the data set of Airbnb we choose, it has 16 variables. Some of the variables are characteristic and some of them are double. We are going to provide three labels for the users to do plot. Firstly, the uses can choose how many variables they will use, we provide the users 3 choices. After they click the box for “one variable”, “two variables”, or “three variables”, the app will jump to the next step. 

### One variable   

For statistics for one variable, the users can choose to make a histogram or frequency polygon. if the variable is double style. If the variable is not double, the users can choose to make a pie chart.  

### Two variables  

For the “two variables” situation, the users can try to observe the relationship between the two variables from the plot they make. The users are able to decide which is for x axis and y axis. They can choose to make a boxplot or scatter plot or a jitter plot. 

### Three variables 

For the “three variables” situation, the users can try to observe the relationship between the two variables from the plot they make. The users are able to decide which is for x axis and y axis.  And they can choose another variable as the facet wrap of the first two variables.   

```{block}
Combine two and three variables and convert language to response and explanatory variables. Be sure to all of logging of either or both variables and to ask if a variable should be converted to a factor

Add a capability for a linear model where the user gets to select three explanatory variables to estimate price (able to log all any or all of them) and show the results of the model with standard errors and their selected house as well as plots for the residuals - at least a residuals versus fitted and QQ plot
```


## Spreadsheet page  

Page 3 contains data tables of the what data we use. It is convenient for the users to have a overall look of the data. 

```{block}
This is easy to do but I wound do last and focus on the statistical analysis


```


# Data Analysis and Visuliaziton/ Statistical Modeling

``` {r, echo = FALSE}
knitr::kable(tibble::tribble(
  ~"variable Type", ~"Plot Tpye", ~"Test type",
  "numeric", "histogram, Density, Frequency Polygon ", "T-test",
  "factor", "pie chart", "NULL",
  "numeric and numeric", "scatter", "Summary",
  "numeric and factor", "boxplot", "ANOVA",
  "factor and factor", "jitter", "Chisq-test",
  "numeric and two factors", "boxplot/facet", "NULL",
  "three factors", "jitter/facet", "NULL",
),
"simple")
```

```{block}
Not sure why you had echo equals FALSE. However, just listing a bunch of options is not statistical analysis. State the question of interest as indicated earlier.
```


# Allocation of Responsibilities for the team  

We plan to have a virtual meeting every week, so and we can share our opinions of the project and change some in detail. Yao is responsible for Page 1. She needs to produce the map after the users filter the data. Shi and Yan are responsible for Page 2 and Page 3. Yan and Shi will produce code for statistical analysis and plot for the uses. For the demonstration and vignette, we will finish it together in a zoom meeting.   

# Project Steps/Schedule  
 
``` {r, echo = FALSE}
knitr::kable(tibble::tribble(
  ~"Project Steps", ~"Complete By Date", ~"   Responsible Individuals",
  "download and tidy the data", "10/30/2020", "Yan",
  "design the UI and what variable to use", "11/3/2020", "Yao, Shi",
  "Creating Shared Repo", "11/22/2020", "Shi",
  "produce the basic panel for shiny app", "11/7/2020", "Yan, Shi",
  "make the plots for shiny app", "11/14/2020", "Yao, Shi",
  "creat the test models for shiny app", "11/22/2020", "Yan, Yao",
  "finish the vignette", "11/28/2020", "Shi",
  "Talk about the Demonstration and practices ", "12/5/2020", "Shi, Yan, Yao"
),
"simple")
```
   
